\documentclass[12pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}

\title{Database Selection Guide}
\author{Integration Test}
\date{\today}

\begin{document}

\maketitle

\chapter{Database Fundamentals}

\section{Database Selection}

\subsection{Database Selection Guide}\label{database-selection-guide}

This section covers how to choose the right database for your application.

\subsection{Key Considerations}\label{key-considerations}

When selecting a database, consider:

\begin{itemize}
\tightlist
\item
\textbf{Data structure}: Structured vs unstructured
\item
\textbf{Consistency requirements}: ACID vs eventual consistency
\item
\textbf{Scale}: Read/write patterns and volume
\item
\textbf{Performance}: Latency and throughput needs
\end{itemize}

\subsection*{Database Selection Quiz}
\vspace{0.3cm}
\noindent
\textbf{Question 1:} Which database should we use when we have unstructured data and there\textquotesingle s a need for high performance?
\\[0.2cm]
\begin{itemize}
 \item \textbf{[CORRECT]} MongoDB
\\[0.1cm]
\textit{Explanation:} 
MongoDB is a database that stores unstructured data and provides high performance in data-relevant operations.
 \item MySQL
 \item Oracle
\end{itemize}
\vspace{0.3cm}
\noindent
\textbf{Question 2:} \textbf{(Select all that apply.)} We should use a key-value database for which scenarios?
\\
\textit{(Select all that apply.)}
\\[0.2cm]
\begin{itemize}
 \item When we create a social network like Facebook with a lot of complex relationships
\\[0.1cm]
\textit{Explanation:} 
A graph database is a suitable option to store a social network with many complex relationships.
 \item \textbf{[CORRECT]} When we need to persist user state in our application
\\[0.1cm]
\textit{Explanation:} 
User states are stored using a key-value database. A user ID can be considered key, and states can be assumed as values.
 \item \textbf{[CORRECT]} When we implement caching in our application
\\[0.1cm]
\textit{Explanation:} 
A cache like Memcached and Redis are key-value stores used for caching in different use-cases.
\end{itemize}

\subsection{Summary}\label{summary}

Choosing the right database is crucial for application success. Consider your data structure, consistency needs, and performance requirements when making your decision.

\end{document}
