\subsection*{Quiz}
\vspace{0.3cm}
\noindent
\textbf{Question 1:} Which database should we use when we have unstructured data and there\textquotesingle s a need for high performance?
\\[0.2cm]
\begin{itemize}
    \item \textbf{[CORRECT]} MongoDB
\\[0.1cm]
\textit{Explanation:} 
MongoDB is a database that stores unstructured data and provides high performance in data-relevant operations.
    \item MySQL
    \item Oracle
\end{itemize}
\vspace{0.3cm}
\noindent
\textbf{Question 2:} When should we avoid choosing a relational database for our application?
\\[0.2cm]
\begin{itemize}
    \item \textbf{[CORRECT]} When we write an application that expects to handle a large number of read-write operations and concurrent users, but strong consistency is not required
\\[0.1cm]
\textit{Explanation:} 
When strong consistency is not required, and there are many read-write operations and concurrent users, a better choice is to use a NoSQL database. Hence
, this is the right option to avoid the relational database.
    \item When we write a financial application, like a stock trading application, and we need our data to be consistent at all times
    \item When we write an application to store a lot of complex structured data
\end{itemize}
\vspace{0.3cm}
\noindent
\textbf{Question 3:} \textbf{(Select all that apply.)} We should use a document-oriented database for which applications?
\\
\textit{(Select all that apply.)}
\\[0.2cm]
\begin{itemize}
    \item \textbf{[CORRECT]} Web-based multiplayer games
\\[0.1cm]
\textit{Explanation:} 
Documents such as JSON and YML store objects in the same structure (as in the game), making the operations within the game easier. Therefore
, such games require document-oriented databases to use.
    \item Banking application requiring consistency
    \item Social network application, like Facebook, containing complex relationships
    \item \textbf{[CORRECT]} Real-time feeds
\\[0.1cm]
\textit{Explanation:} 
The real-time feed contains variably structured data (one feed can have different components than the others) for which a document database is a suitable option.
\end{itemize}